PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-08 paper/app-lumis.tex
App B - still not complete

\begin{table}[!t]
  \centering
  \tiny
  \input{tables/TableB1.tex}\\
  \caption{The 34 parton luminosities contributing to the predictions, accurate
    to NLO QCD+EW, of the Drell--Yan lepton-pair production measured by the
    ATLAS experiment at a centre-of-mass energy of
    \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The ten largest contributions
    to the cross section (irrespective of their sign) are reported, in
    percentage, for each bin. Empty spaces typically denote contributions
    smaller than a fraction of percent. The bin edges are in the invariant mass
    of the lepton pair, $M_{\ell\bar\ell}$, as follows: 116, 130, 150, 170, 190,
    210, 230, 250, 300, 400, 500, 700, 1000, 1500 [GeV].
  }
  \label{tab:B1}
\end{table}

>>>>

In this appendix, we present the complete breakdown of parton luminosities
entering the NLO QCD+EW predictions of the various measurements
considered in section~\ref{sec:results}. For each parton luminosity,
we indicate its percentage contribution to the cross section in a given bin.
In particular:
\begin{itemize}
\item Table~\ref{tab:B1} collects the thirty-five parton luminosities
  contributing to the Drell--Yan lepton-pair production measured by the
  ATLAS experiment at a centre-of-mass energy of
  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}.
  The thirteen bins are for the invariant mass of the lepton pair,
  $M_{\ell\bar\ell}$, with edges at 116, 130, 150, 170, 190,
  210, 230, 250, 300, 400, 500, 700, 1000 and 1500 GeV.
\item Tables~\ref{tab:B2}-\ref{tab:B7} collect the thirty-five parton
  luminositites contributing to the double differential Drell--Yan lepton-pair
  production measured by the CMS experiment at a centre-of-mass energy of
  \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The one hundred and thirty-two
  bins are split across tables~\ref{tab:B2}-\ref{tab:B7}, where each table
  corresponds to a bin in the invariant mass of the lepton pair:
  table~\ref{tab:B2} to  $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; table~\ref{tab:B3} to  $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$; table~\ref{tab:B4} to  $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$; table~\ref{tab:B5} to  $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$; table~\ref{tab:B6} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$; and table~\ref{tab:B7} to $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$. In each table, the bins are in the rapidity of the lepton pair, $0.0<y_{\ell\bar\ell}<2.4$, and each of them has a width of 0.1 (0.2 in the largest invariant mass range).
\item Table~\ref{tab:B8} collects the thirty-seven parton luminosities
  contributing to the top-quark pair distributions measured by the ATLAS and
  CMS experiments at a centre-of-mass energy of
  \SI{8}{\tera\electronvolt}~\cite{Aad:2015mbv,Khachatryan:2015oqa}.
  The four distributions, differential in the transverse momentum of the top
  quark,  $p_\mathrm{T}^\mathrm{t}$, in the rapidity of the top quark,
  $y_\mathrm{t}$, in the invariant mass of the top-quark pair,
  $m_{\mathrm{t}\bar{\mathrm{t}}}$, and in the rapidity of the top-quark pair,
  $y_{\mathrm{t}\bar{\mathrm{t}}}$ are shown. The bin edges are, respectively:
  0, 60, 100, 150, 200, 260, 320, 400, 500~GeV; 0.0, 0.4, 0.8, 1.2, 1.6, 2.5;
  345, 400, 470, 550, 650, 800, 1100, 1600~GeV;
  and 0.0, 0.3, 0.6, 0.9, 1.3, 2.5.
\item Table~\ref{tab:B9} collects 
\end{itemize}

%-------------------------------------------------------------------------------
\begin{table}[!t]
  \centering
  \tiny
  \input{tables/TableB1.tex}\\
  \caption{The 35 parton luminosities contributing to the predictions, accurate
    to NLO QCD+EW, of the Drell--Yan lepton-pair production measured by the
    ATLAS experiment at a centre-of-mass energy of
    \SI{7}{\tera\electronvolt}~\cite{Aad:2013iua}. The contributions
    are reported, in percentage, for each of the thirteen bins. The bin edges
    are in the invariant mass of the lepton pair, $M_{\ell\bar\ell}$, as follows:
    116, 130, 150, 170, 190,
    210, 230, 250, 300, 400, 500, 700, 1000, 1500 GeV.}
  \label{tab:B1}
\end{table}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB2.tex}\\
  \caption{The 35 parton luminositites contributing to the predictions, accurate
    to NLO QCD+EW, of the double differential Drell--Yan lepton pair production
    measured by the CMS experiment at a centre-of-mass energy of
    \SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}. The invariant mass
    bin is $\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$; bins 1-24 are in the rapidity of the lepton pair,
  $0.0<y_{\ell\bar\ell}<2.4$, and each bin has a width of 0.1.}
  \label{tab:B2}
\end{table}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB3.tex}\\
  \caption{Same as table~\ref{tab:B2}, but for the invariant mass bin
    $\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$.}
  \label{tab:B3}
\end{table}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB4.tex}\\
    \caption{Same as table~\ref{tab:B2}, but for the invariant mass bin
    $\SI{45}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{60}{\giga\electronvolt}$.}
  \label{tab:B4}
\end{table}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB5.tex}\\
    \caption{Same as table~\ref{tab:B2}, but for the invariant mass bin
    $\SI{60}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{120}{\giga\electronvolt}$.}
  \label{tab:B5}
\end{table}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB6.tex}\\
    \caption{Same as table~\ref{tab:B2}, but for the invariant mass bin
    $\SI{120}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{200}{\giga\electronvolt}$.}
  \label{tab:B6}
\end{table}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{table}[!t]
  \centering
  \tiny
  \input{tables/TableB7.tex}\\
    \caption{Same as table~\ref{tab:B2}, but for the invariant mass bin
      $\SI{200}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{1500}{\giga\electronvolt}$. Each bin in the rapidity of the lepton pair has a width of 0.2.}
  \label{tab:B7}
\end{table}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\begin{table}[!p]
  \centering
  \tiny
  \input{tables/TableB8.tex}\\
  \input{tables/TableB9.tex}\\
  \caption{}
  \label{tab:B1}
\end{table}
%-------------------------------------------------------------------------------
